Scalar on Function Regression

### 2022-01-03 Presentation/slides.tex
Estimation

		Assume that we have a data set containing observations each of which is made up of:
		\begin{itemize}
			\item $y_i$: \quad a scalar realizations of $Y$
			\item $f_i(t)$: \quad a realization of $F$
		\end{itemize}

@@

	\begin{frame}
		$$\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
		This is a scalar we can calculate for each observation and for each deterministic basis function $b_j(t)$.
	\end{frame}

>>>>

		Assume that we have a data set containing observations each of which is made up of:
		\begin{itemize}
			\item $y_i$: a scalar realization of $Y$
			\item $f_i(t)$: a realization of $F$
		\end{itemize}

@@

	\begin{frame}{Estimation via Basis Representation}
		$$Z_j(\omega) = \int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
		This is a scalar random variable for which we can calculate a realization for each observation $f_i(t)$ and for each deterministic basis function $b_j(t)$.
		$$Z_{i,j} = \int_{0}^{1} f_i(s) b_j(s)\mathrm{d}s$$
		Leading to the following transformation
		$$Y(\omega) = \alpha + \sum_{j = 1}^{\infty} \psi_j Z_j(\omega) + \epsilon(\omega)$$

	\begin{frame}{Estimation via Basis Representation}
		This allows us to write each observation in the data set as
		\begin{itemize}
			\item $y_i$: a scalar realization of $Y$
			\item $\left(Z_{i,j}\right)_{j \in \mathbb{N}}$: a countably infinite sequence of scalars
		\end{itemize}
		\vspace{0.2cm}

		Truncating the functional basis allows us to approximate the data set in the usual multivariate form.
		\begin{itemize}
			\item $y_i$: a scalar realization of $Y$
			\item $\left(Z_{i,1} \: \dots \:  Z_{i,L} \right)'$: a vector of scalar regressors
		\end{itemize}
		\vspace{0.2cm}

		Coefficients can then be estimated using theory from multivariate regression leading to an estimated coefficient vector $\hat{\beta}_L \in \mathbb{R}^L$.
	\end{frame}

	\begin{frame}{Estimation via Basis Representation}
		This can then be translated into an estimated coefficient function $\hat{\beta}(t)$ via:
	\end{frame}
